Supporting Information for Coherent IR-Hyper-Raman Four Wave Mixing Spectroscopy

### 2024-10-01 si.tex
Fixed contour integration
Made much clearer when you can use this trick.

In addition to the linewidth and offset impacting the shape of the HDFG response, the sign of the molecular parameters $M^{ge}_0, \Lambda^{ge}_0, \frac{\partial M^{ge}}{\partial Q} , \frac{\partial \Lambda^{ge}}{\partial Q}$ will significantly impact the HDFG spectrum.
As discussed in the main text, the atypical lineshape in the post-resonance region of the HDFG region arises due to the sign of all four aforementioned parameters being identical.
Changing the sign of one (or three) parameters will change the sign of $A, B$ and eliminate interference between the real and imaginary terms.  
As an example, we demonstrate the resultant HDFG spectrum when $M_0^{ge} < 0$, and all other terms $>0$ (\autoref{fig:chgsign}).
Compared to Figure 3 of the main text, the contributions from the $A, B_1$ and $B_2$ terms to $\Re(\gamma)$ and $\Im(\gamma)$ significantly change.
In particular, $\Re(\gamma)$ and $\Im(\gamma)$ are of similar value in the post-resonance region, eliminating the interference seen in Figure 3 of the main text.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/drsive_chgsign.png}
	\caption{Contributions of $A, B$ to HDFG spectrum for a simple two harmonic well system, identical to the main text, except $M_0^{ge} < 0$.
		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\Delta = 0.5$, $\omega_1 = \omega_{g1, g0}$, (c, d) real and imaginary parts of terms plotted in (b), respectively.
		The spectra are referenced to $\max{(A+B)}$. 
		The vibronic one and two photon absorption operators are scaled such that $\abs{B}/\abs{A} \sim$ 0.1, following Chung and Ziegler. \cite{Ziegler1988}
} 
	\label{fig:chgsign}
\end{figure}

\section{Evaluating impact of static inhomogeneity on HDFG output}
In this section, the integral
\begin{equation}\label{generalcontour}
	\begin{split}
		\gamma_{ijkl} &= \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi)\\
		&= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\eta_{ijkl}}{\left(\Delta_{ga} - \xi\right)\left(\Delta_{ba}+ c\xi\right)} \\
		&= \frac{\eta_{ijkl} \sigma}{\pi} \int_{-\infty}^\infty \mathrm{d}\xi\frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} + c\xi}\\
	\end{split}
\end{equation}
is evaluated for $c=-1$ (electronic state and vibrational state energy fluctuations are anti-correlated) and $c=1$ (electronic state and vibrational state energy fluctuations are correlated).
Integrals such as those found in \autoref{generalcontour} can be evaluated by using the Residue theorem. %@dan i had too much white space, needed something to fill in... delete if you want.
Recall that if an analytic, complex valued function $f(z)$ is integrated along a positively oriented closed contour,%guessing on this one
\begin{subequations}\label{eq:generalcontour}
	\begin{equation}
		\oint \mathrm{d}z f(z) = 2\pi i \sum_k \Res[f(z_k)]
	\end{equation}
where the residue of an n$^{\text{th}}$ order pole at $z = z_k$, $\Res[f(z_k)]$ is evaluated as
	\begin{equation}
		\Res[f(z_k)] = \lim_{z \rightarrow z_k} \frac{1}{\left(n-1\right)!} \frac{\mathrm{d}^{n-1}}{\mathrm{d}z^{n-1}} \left[f(z) (z-z_k) \right]
	\end{equation}
For first order poles (the cases considered below), $n=1$, so that 
	\begin{equation}
		\oint \mathrm{d}z f(z) = 2\pi i \sum_k \lim_{z \rightarrow z_k} f(z) (z-z_k)
	\end{equation}
\end{subequations}
Note that in \autoref{eq:generalcontour}, the integrals are closed along a contour which wraps all the poles. 
In the case where the integration is only needed along the real axis, the contour can be drawn as a semicircle in the positive half of the complex plane. \cite{MorseFeshbach}

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/corr_contour.png}
	\caption{Poles (blue dots) and contours (black lines) used to evaluate \autoref{generalcontour} for (a) anti-correlated ($c=-1$) and (b) correlated ($c=1$) modes. 
	} 
	\label{fig:contours}
\end{figure}
\break

>>>>

In addition to the linewidth and offset impacting the shape of the HDFG response, the sign of the molecular parameters $M^{ge}_0, \Lambda^{ge}_0, \frac{\partial M^{ge}}{\partial Q} , \frac{\partial \Lambda^{ge}}{\partial Q}$ will significantly impact the HDFG spectrum.
As discussed in the main text, the atypical lineshape in the post-resonance region of the HDFG region arises due to the sign of all four aforementioned parameters being identical.
Changing the sign of one (or three) parameters will change the sign of $A, B$ and eliminate interference between the real and imaginary terms.  
As an example, we demonstrate the resultant HDFG spectrum when $M_0^{ge} < 0$, and all other terms $>0$ (\autoref{fig:chgsign}).
Compared to Figure 3 of the main text, the contributions from the $A, B_1$ and $B_2$ terms to $\Re(\gamma)$ and $\Im(\gamma)$ significantly change.
In particular, $\Re(\gamma)$ and $\Im(\gamma)$ are of similar value in the post-resonance region, eliminating the interference seen in Figure 3 of the main text.
\newpage
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/drsive_chgsign.png}
	\caption{Contributions of $A, B$ to HDFG spectrum for a simple two harmonic well system, identical to the main text, except $M_0^{ge} < 0$.
		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\Delta = 0.5$, $\omega_1 = \omega_{g1, g0}$, (c, d) real and imaginary parts of terms plotted in (b), respectively.
		The spectra are referenced to $\max{(A+B)}$. 
		The vibronic one and two photon absorption operators are scaled such that $\abs{B}/\abs{A} \sim$ 0.1, following Chung and Ziegler. \cite{Ziegler1988}
} 
	\label{fig:chgsign}
\end{figure}
\pagebreak
\section{Evaluating impact of static inhomogeneity on HDFG output}
In this section, the integral
\begin{equation}\label{generalcontour}
	\begin{split}
		\gamma_{ijkl} &= \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi)\\
		&= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\eta_{ijkl}}{\left(\Delta_{ga} - \xi\right)\left(\Delta_{ba}+ c\xi\right)} \\
		&= \frac{\eta_{ijkl} \sigma}{\pi} \int_{-\infty}^\infty \mathrm{d}\xi\frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} + c\xi}\\
	\end{split}
\end{equation}
is evaluated for $c=-1$ (electronic state and vibrational state energy fluctuations are anti-correlated) and $c=1$ (electronic state and vibrational state energy fluctuations are correlated).

Integrals such as \autoref{generalcontour} can be evaluated by using the Residue theorem.\cite{MorseFeshbach}
For clarity, we briefly outline the technique.
%@dan i had too much white space, needed something to fill in... delete if you want.
Consider the integral
\begin{equation}
	\int_{-\infty}^{\infty} \mathrm{d}x f(x)
\end{equation}
If $\int_{-\infty}^{\infty} \mathrm{d}x f(x)$ exists %is this strict enough?
and $f(z)$ is an analytic function, where $z$ is a complex variable, then
\begin{subequations}\label{eq:generalcontour}
	\begin{equation}
		\int_{-\infty}^{\infty}  \mathrm{d}x f(x) = 2\pi i \sum_k \Res[f(z_k)]
	\end{equation}
where $\Res[f(z_k)]$ refers to the residue of $f(z)$ in the upper half of the complex plane at the pole $z_k$ and the sum is taken over all the poles, i.e., non-removable singularities, of $f(z)$.
Note that the residue of an n$^{\text{th}}$ order pole at $z = z_k$ is evaluated as
	\begin{equation}
		\Res[f(z_k)] = \lim_{z \rightarrow z_k} \frac{1}{\left(n-1\right)!} \frac{\mathrm{d}^{n-1}}{\mathrm{d}z^{n-1}} \left[f(z) (z-z_k)^n \right]
	\end{equation}
For first order poles (the cases considered below), $n=1$, so that 
	\begin{equation}
		\int_{-\infty}^{\infty} \mathrm{d}x f(x) = 2\pi i \sum_k \lim_{z \rightarrow z_k} f(z) (z-z_k)
	\end{equation}
\end{subequations}
Note that in \autoref{eq:generalcontour}, the integrals are closed along a contour which wraps all the poles in the positive half of the complex plane.

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/corr_contour.png}
	\caption{Poles (blue dots) and contours (black lines) used to evaluate \autoref{generalcontour} for (a) anti-correlated ($c=-1$) and (b) correlated ($c=1$) modes. 
	} 
	\label{fig:contours}
\end{figure}
